The shape of kelp: environmental influences on kelp morphology

### 2018-11-20 chapter_2.Rmd
commit

# fix incorrect

@@

```{r, echo= FALSE, message=FALSE, warning=FALSE, results="hide", fig.cap="A correlation graph depicting the relationships that various temperature and wave parameters share, at an annual timescale. The left Y-axis as well as bottom X-axis represent the measurements for the parameters, while the top X-axis and right Y-axis depict the abiotic parameter name. The top right section of the graph represents correlation coefficients between abiotic parameters. The bottom left section provides individual linear regressions between each abiotic parameter, with a fitted line. Each point of each linear graph represents a collection site. The diagonal density plots represent the spread of the data for each abiotic relationship.", fig.height=8, fig.width=12, fig.pos="H"}
# # ggpairs to plot correlation coefficients
# # Annual
ggpairs(data = ann_abio_cor, columns = 2:14, 
        upper = list(continuous = wrap("cor", size = 3)), 
        lower = list(continuous = "smooth"), 
        diag = list(continuous = "densityDiag")) + 
  theme(text = element_text(size = 9)) + 
  ggtitle("Annual")

@@

# # August
ggpairs(data = aug_abio_cor, columns = 2:14, 
        upper = list(continuous = wrap("cor", size = 3)), 
        lower = list(continuous = "smooth"), 
        diag = list(continuous = "densityDiag")) + 
  theme(text = element_text(size = 9)) + 
  ggtitle("August")

@@

# # February
ggpairs(data = feb_abio_cor, columns = 2:14, 
        upper = list(continuous = wrap("cor", size = 3)), 
        lower = list(continuous = "smooth"),
       diag = list(continuous = "densityDiag")) + 
  theme(text = element_text(size = 9)) + 
  ggtitle("February")

>>>>

@@

```{r, echo= FALSE, message=FALSE, warning=FALSE, results="hide", fig.cap="A correlation graph depicting the relationships that various temperature and wave parameters share, at an annual timescale. The left Y-axis as well as bottom X-axis represent the measurements for the parameters, while the top X-axis and right Y-axis depict the abiotic parameter name. The top right section of the graph represents correlation coefficients between abiotic parameters. The bottom left section provides individual linear regressions between each abiotic parameter, with a fitted line. Each point of each linear graph represents a collection site. The diagonal density plots represent the spread of the data for each abiotic relationship.", fig.height=8, fig.width=12, fig.pos="H"}
## ggpairs to plot correlation coefficients
## Annual
ggpairs(data = ann_abio_cor, columns = 2:14, 
        upper = list(continuous = wrap("cor", size = 3)), 
        lower = list(continuous = "smooth"), 
        diag = list(continuous = "densityDiag")) + 
  theme(text = element_text(size = 9)) + 
  ggtitle("Annual")

@@

## August
ggpairs(data = aug_abio_cor, columns = 2:14, 
        upper = list(continuous = wrap("cor", size = 3)), 
        lower = list(continuous = "smooth"), 
        diag = list(continuous = "densityDiag")) + 
  theme(text = element_text(size = 9)) + 
  ggtitle("August")

@@

## February
ggpairs(data = feb_abio_cor, columns = 2:14, 
        upper = list(continuous = wrap("cor", size = 3)), 
        lower = list(continuous = "smooth"),
       diag = list(continuous = "densityDiag")) + 
  theme(text = element_text(size = 9)) + 
  ggtitle("February")
